04_DESeq_sexes

### 2019-07-19 analysis/04_DESeq2_sexes.Rmd
better names

```{r totalDEGbarsplots}
g <- plotserialDEGs(DEGs.female_hypothalamus, "Female hypothalamus")
h <- plotserialDEGs(DEGs.female_pituitary, "Female pituitary")
i <- plotserialDEGs(DEGs.female_gonad, "Female gonad")
j <- plotserialDEGs(DEGs.male_hypothalamus, "Male hypothalamus")
k <- plotserialDEGs(DEGs.male_pituitary, "Male pituitary")
l <- plotserialDEGs(DEGs.male_gondad, "Male gonad")

@@

pdf("../figures/sexes/totalDEGbarsplots-1.pdf", width = 10, height = 6)
plot(mybarplots)
dev.off()
```

>>>>

```{r characterization}
g <- plotserialDEGs(DEGs.female_hypothalamus, "Female hypothalamus", "#00A08A")
h <- plotserialDEGs(DEGs.female_pituitary, "Female pituitary", "#00A08A")
i <- plotserialDEGs(DEGs.female_gonad, "Female gonad", "#00A08A")
j <- plotserialDEGs(DEGs.male_hypothalamus, "Male hypothalamus", "#F98400")
k <- plotserialDEGs(DEGs.male_pituitary, "Male pituitary", "#F98400")
l <- plotserialDEGs(DEGs.male_gondad, "Male gonad", "#F98400")

@@

pdf("../figures/sexes/characterization-1.pdf", width = 10, height = 6)
plot(mybarplots)
dev.off()
```

```{r manipulation}
